---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# powers

The goal of powers is to perform basic computations on numeric vectors.
This package has four exported functions: `Box_Cox()`, `log()`, `cube()` and `square()`. There is one internal function `pow()`. These functions only work for numeric inputs. 

* Box_Cox( ): This function performs the box cox transform of inputs. 

* log( ): This function performs log transformation of inputs.

* cube( ): This function takes inputs to the power of 3.

* square( ): This function takes inputs to the power of 2.

## Installation

You can install powers from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("QinxinLin/powers")
```

## Example

Firstly, I need to load `powers` package.

```{r,message=FALSE}
library(powers)
```

**(1) Examples of `Box_Cox()` function**

```{r}
#inputs without NA
num<-c(-1,4,3,-3,-5)
Box_Cox(num,3,6)
#inputs with NA
num<-c(-1,4,3,-3,-5,NA)
Box_Cox(num,2,7,na.omit = TRUE)
Box_Cox(num,2,7,na.omit = FALSE)
```

**(2) Examples of `log()` function**

```{r}
#inputs without NA
num<-c(4,3,8,5)
log(num,2)
#inputs with NA
num<-c(4,3,8,5,NA)
log(num,2,na.omit = TRUE)
log(num,2,na.omit = FALSE)
```

**(3) Examples of `square()` function**

```{r}
#numeric inputs
num<-c(4,3,8,5)
square(num)
#non-numeric inputs
num<-c(4,3,8,5,"a")
square(num)
```

**(4) Examples of `cube()` function**

```{r}
num<-c(4,3,8,5)
cube(num)
#non-numeric inputs
num<-c(4,3,8,5,"a")
cube(num)
```

## For Developers

Use the internal pow function as the machinery for the front-end functions such as Box_Cox, log, square and cube.
